### 2022-10-02 official_document_thesis/front/template/signatures.tex

\pagestyle{empty}

\begin{large}
\setlength{\parindent}{0pt}
\begin{center}

{\large\bf به نام خدا}

\ThesisUniversity

\vspace{-0.1cm}
\ThesisDepartment

\vspace{2.5em}
\textbf{\large\ThesisType}

\end{center}

\vspace{3em}

{\large عنوان: \ThesisTitle}

\vspace{.3em}

{\large نگارش: \ThesisAuthor}

\textbf{کمیته‌ی ممتحنین}

\begin{tabular}{p{7cm}r}
استاد راهنما: سامان مقیمی عراقی & امضاء:
\includegraphics[width=3cm]{Figures/saman_sign.png}
 \\[1em]
استاد ممتحن: محمدرضا رحیمی‌تبار& امضاء:
\includegraphics[width=3cm]{Figures/rahimitabar_sign.png}
\\[1em]
استاد ممتحن: محمد دهقان نیری & امضاء:
\includegraphics[width=3cm]{Figures/niri_sign.png}
 \\[1em]
& تاریخ:
\end{tabular}

\end{large}

\newpage